---
title: "Lab Week 8"
author: "Claire Powers"
date: "3/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load packages
```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)
```

### Column graph of Texas oil spills
```{r}
oil_spills <- read_csv("oil_spills.csv")

df <- oil_spills %>% 
  filter(`Accident State`=="TX" & `Accident Year`< 2017) %>% 
  group_by(`Accident Year`) %>% 
  summarise(Loss = sum(`Net Loss (Barrels)`))

colnames(df) <- c("Year","Loss")

#Column graph of loss over years
ggplot(df, aes(x=Year, y =  Loss))+
  geom_col()

```

### Leaflet plot of spill locations in texas in 2016.
```{r}
df_loc <- oil_spills %>% 
  filter(`Accident State`=="TX" & `Accident Year` == 2016) %>% 
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc) <- c("Latitude","Longitude","Net_Loss")

oil_sf <- st_as_sf(df_loc, coords = c("Longitude","Latitude"), crs=4326)

leaflet(oil_sf) %>% 
  addTiles() %>% 
  addMarkers()
```

## tmap plot with the Texas state shapefile
```{r}
states <- st_read(dsn=".", layer = "states")

tex_border <- states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326)

plot(tex_border)

tm_shape(tex_border) + 
  tm_polygons() +
  tm_shape(oil_sf)+
  tm_dots(size = 0.3)
```
### Convert the data to spatial point patterns(combination of the point data and the bounding window)

-Have to convert this into point patter data with a window. This is an area of r with lots of potential, likely going to be more streamline soon. 
```{r}
# Convert back from sf into df type data
spill_sp <- as(oil_sf,"Spatial")
spill_ppp <- as(spill_sp,"ppp")

#class(spill_ppp)

# If we're going to do point pattern anaylysis we need to know where the points are, and what out window bounds are. 

tx_sp <- as(tex_border, "Spatial")
tx_owin <- as(tx_sp, "owin")

# Combine these two things so that R can see the complete picture at once. 

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)
```

###A density plot:
```{r}
plot(density(all_ppp, sigma = 0.4))
```


### Quadrat test for spatial evenness
```{r}
oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5)
oil_qt
```

## Super small p - value, reject the null hypothesis that data are CSR.

```{r}
plot(all_ppp)
plot(oil_qt, add=TRUE, cex = 0.4)
```

## On the right, how many counts you would expect with CSR, on the left, how many were observed, and on the bottom, a standardized metric for the different between the expected cound and actual count. 

## G-function for Nearest Neighbor Analysis. 
```{r}
r <- seq(0,1, by = 0.01)
#Calculate for existing point pattern data calculate the g-function. 
#Need to simulate CSR data to create something to compare our data to. If these were truly spatially random, what would they look like? 

oil_gfun <- envelope(all_ppp, fun = Gest, r = r, nsim = 100)

#plot the outsomes. What's stored in this is r(the lag for each of the values from .01 to 1), obs = how many values we within that distance, divided by the total number of observations. Theo is the theoretical value if points are CSR.

ggplot(oil_gfun, aes(x = r, y = obs)) +
  geom_line(color = "black") +
  #compare to CSR 
  geom_line(aes(x=r, y = theo), color = "red")
  
#Our data has a higher proportion of point pairs with lower distances between each other, than would exist in a CSR set of points. 
```

###Nearest neighbor using the L-function (Ripley's K, standardized)
```{r}

r2 <- seq(0,4, by = 0.1)

oil_lfun <- envelope(all_ppp, fun = Lest, r = r2, nsim = 20, global = TRUE)

ggplot(oil_lfun, aes(x = r2, y = obs)) +
  geom_line(color = "black") +
  geom_line(aes(x = r2, y = theo), color = "blue")

```

